The problem and promise of scale in multilayer networks

### 2020-01-24 paper/manuscript.Rmd
Update manuscript.Rmd
soc scale
scale section

We generated seasonal multilayer social networks consisting of habitat-specific monolayers. Each layer was the social association network generated in one of three habitat types (lichen, open, and closed). For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION).

Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another. Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al. 2019). Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises et al. 2018). To assess the role of social scale in multilayer networks, we varied the threshold distance for group assignment between 5-500m (see *Social scale* section below). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.

@@

### Scale in multilayer networks

@@

#### Altering social scale

@@

#### Altering observational scale

@@

## Scale in multilayer networks in practice: case study results

>>>>

We generated seasonal multilayer social networks consisting of habitat-specific monolayers. Each layer was the social association network generated in one of three habitat types (lichen, open, and closed). For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al. 2019) in *R version* (R Core Team 2020).

Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another. Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al. 2019). Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.

@@

### Varying scale in multilayer networks

@@

#### Social scale

@@

#### Observational scale

@@

## Scale in multilayer networks in practice: case study results and discussion

Results and interpretation of temporal scale - balh

Results and interpretation of spatial scale - blah blah

Results and interpretation of social scale - blah blah blah
